Stability of variational quantum dynamics with Gaussian approximants

### 2013-07-15 paper.tex
writing

>>>>

There are now three goals for optimisation of $\dot z$:
\item{1.} The ket $|ψ(z)〉$ solves Schrödinger's equation.  I.e., $|Dψ(z)〉\dot z=H|ψ(z)〉$.
\item{2.} Singular vectors of $|Dψ〉$ belonging to small singular values do not dominate the solution.  This is controlled by a Tychonov condition, $\dot z=0$, or perhaps by truncation.
\item{3.} The condition of $|A(z)〉$ improves.  This can be set up as a least squares condition $Dσ_R(z)\dot z+Cσ_R(z)\dot z*=|σ_R||\dot z|_{\rm opt}$, given a desired rate of change of $z$.  No doubt there is a better way.

Putting these conditions together, with regularisation parameters $λ$ and $ε$, gives the problem
$$\pmatrix{|Dψ(z)〉& 0 \cr λI & 0 \cr Dσ_R(z) & Cσ_R(z)}
	\pmatrix{\dot z\cr \dot z*} =
	\pmatrix{H|ψ(z)〉\cr 0\cr |σ_R||\dot z|_{\rm opt}}.$$
This raises a technical problem, because we need to constrain $\dot z*$ to be the conjugate of $\dot z$.  Alternatively, if we write $z=x+iy$, we need to solve a complex least squares problem under the constraint that the solution is real.  Neither of those sounds trivial, but it shouldn't be impossible.
